Denoising and Covariance Estimation of Cryo-EM Images

### 2017-02-10 echo_talk.tex
Echo talk

>>>>

\section{What is cryo electron microscopy?}

\begin{frame}<beamer>
\frametitle{Why cryo-EM?}

%  FEI
\begin{itemize}
 \item 3D structure of macromolecules - understand function - drug discovery for cancer, AIDS, HIV, etc.
 \item X ray crystallography: many proteins, viruses resistant to crystallization (HIV virus)
 \item Cryo-EM: native state
 \item Can study structures impossible before!
\end{itemize}
\end{frame}

\begin{frame}<beamer>
\frametitle{Nature Method of the Year 2015}
\includegraphics[width=0.5\textwidth]{nature.png}%
\end{frame}

\begin{frame}<beamer>
\frametitle{Cancer}
\includegraphics[width=0.5\textwidth]{cancer.png}%
\end{frame}

\begin{frame}<beamer>
\frametitle{Zika}
\includegraphics[width=0.5\textwidth]{zika.png}%
\end{frame}

\section{Cryo-EM Pipeline}
\begin{frame}
\frametitle{3D from 2D}
%  FEI
\begin{itemize}
 \item Flash freeze sample in an ice layer
 \item Image with an electron microscope
 \item 2D images at unkown orientations -> 3D structure
 \item Sounds like Structure from Motion (SfM)?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Sounds like SfM?}
%  FEI
\includegraphics[width=0.5\textwidth]{zika.png}%
\begin{itemize}
  \item Can't detect features from raw images, unlike SfM
 \item Need new algorithms to handle noise level!
\end{itemize}
\end{frame}
